Scikit-learn: machine learning without learning the machinery

### 2014-11-06 article.tex
cosmetics (mostly re-aligning in the example script)

\author[1]{G. Varoquaux\thanks{gael.varoquaux@inria.fr}}
\author[2]{L. Buitinck}
\author[3]{G. Louppe}
\author[1]{O. Grisel}
\author[1]{F. Pedregosa}
\author[4]{A. Mueller}
\affil[1]{Parietal, INRIA, Bat 145 CEA Saclay, 91191 Gif-sur-Yvette,
France}
\affil[2]{ISLA, University of Amsterdam, Science Park 904, Amsterdam, The
Netherlands}
\affil[3]{Systems and Modeling Research Unit, University of Liège
Montefiore Institute (B28), Liège, Belgium}
\affil[4]{Amazon Development Center Germany, Berlin, Germany}

@@

Scikit-learn aims at bridging the gap between machine-learning research and
applications by providing a library, and not an environment, in a
general-purpose language, relying on domain-agnostic data structures
\cite{pedregosa2011}. Emphasis is put on quality and ease of use, which
implies focus on installation issues, documentation, and API design
\cite{buitinck2013ecml}. For the project to be usable in real-world
settings, computational performance is also a priority.

@@

\paragraph{Supervised models: learning to predict.}
%
The goal of supervised models is prediction of some value of interest.
The corresponding estimators
have a {\tt predict} method, that takes a data matrix $\mathbf{X}$ and
returns a predicted $\mathbf{y}$.

\paragraph{Model evaluation and parameter selection.}
%
The performance of a model measures its ability to correctly
predict new data. Because of overfitting, the \emph{train} data used for
learning
should in general not be used to also evaluate model performance, as it may often
result in overly optimistic estimates of the true prediction error of the model.
Instead, the correct way to obtain an unbiased estimate is to leave out \emph{test} data,
untouched during training and used for model evaluation only.
Alternatively, a \emph{cross-validation} scheme may also be
used, where the data is repeatedly split into \emph{train} and
\emph{test} subsets. Scikit-learn provides integrated support for
cross-validation. Specific iterators can specify the train and test
subsets. Several functions and objects accept these iterators as arguments to
perform cross-validation internally. For instance the {\tt
cross\_val\_score} function measures the prediction score of an
estimator. Cross-validation can also be used to tune the meta-parameters
of an estimator, such as the sparsity of a sparse model. For this,
specific estimators, \emph{meta-estimators}, such as the {\tt
GridSearchCV}, take another estimator at construction time, and use
cross-validation internally to set its parameter. When used together with
{\tt cross\_val\_score}, they perform \emph{nested} cross-validation,
\emph{i.e.}~the meta-parameters are set independently of the test data.

@@

In Fig.~\ref{fig:code} we give an example of fully functioning code to
do sentiment polarity classification for movie reviews: given a review,
it outputs whether the review is positive about the movie it concerns.
The code demonstrates the use of pipelines, and also shows how machine
learning ties into other Python modules: downloading, unpacking and
learning from a dataset are all done in one programming language.
This script first fetches a hand-labeled movie review dataset
\cite{pang2004} and unpacks it to disk using standard Python libraries.
It then loads these using scikit-learn data loading functions, makes a
pipeline of a \textsf{tf--idf} feature extractor
\cite{rennie2003tackling} (that turns strings into a sparse matrix based
on word frequencies) and logistic regression, and finally trains the
model. Parameters for the feature extractor and the classifier
were set manually.

@@

% The citation is for "Heaps' law":
% vocabulary size as a function of collection size.
% Gael, feel free to remove it if you think it's too detailed.
With large collections of text, one faces both challenges:
the dimensionality $p$
tends to increase with sample size $n$, as the number of different words used
is greater in large collections \cite[88--89]{manning2009}.
Beyond the mere size of the data matrix
created by a standard vectorization approach, outlined earlier, another challenge
is that the vectorization must be done in two passes over the documents,
as the size of the output vectors is not known up front.
Here, \emph{feature hashing} can be used
to tackle both of these challenges and produce a streaming vectorizer,
the {\tt HashingVectorizer} in scikit-learn.
Words are run through a (stateless) hash function, rather than a lookup table,
to map words to indices.
Collisions may occur, but the hashing algorithm \cite{weinberger2009}
is specially designed to mitigate their effect.
The dimensionality of the output vectors can be set by the user;
the bigger, the less likely collisions will occur.

@@

Scikit-learn has become a reference machine learning toolkit. As such, it
should offer a wide variety of learning algorithms. However, each new
feature, each new line of code, comes with a maintenance cost.
Uncontrolled growth would lead the project to pick up weight until it
came to a crawl. The difficulty lies in defining the project scope and
prioritizing methods. We strive to identify and integrate all major
methods most useful for prediction tasks. We favor time-tested
algorithms and put great care in the choice of default parameters. We put
a lot of effort in making the documentation didactic and
pragmatic. Our
secret ambition is that it can provide an executable alternative to
textbooks, with all the figures are generated by code examples.

Machine learning is a very active field of research, with promising
trends such as deep learning, harnessing GPUs or distributed computing
for extra computational power, or extending to new platforms, such as
Android or iOS-based embedded devises. However, as scikit-learn's purpose
is to provided tried-and-true, mostly turn-key, predictive tools, we have
to walk the fine line between supporting powerful techniques and
utilizing our limited project cycles on proven technologies. For
instance, deep neural networks are an emerging tool with a huge
potential, but are still in flux and hard to use without significant expertise.
Similarly, GPGPU technology is promising, but not ready for non-expert use.
The HPC community and industry have largely achieved source-level compatibility with OpenCL
\cite{stone2010opencl},
but performance portability and cross-platform driver support remain
challenging.
%
Support for mobile platforms such as Android is determined by those platforms'
support for Python and the standard C/C++ build chain. Indeed, our basic
execution environment is the scientific Python stack, that is both very
powerful and high-level. The vision of the scikit-learn project is to
bring advances in machine learning to users that that may lack the full
expertise. As a consequence, we focus on seasoned approaches, rather than
implementing ongoing research. We believe that code is an intrinsic part
of the scholarship outcome of scientific research in computational
science \cite{buckheit1995wavelab}, and scikit-learn strives to be akin
to a reference textbook in this research software landscape.

>>>>

\author[1]{G. Varoquaux\thanks{gael.varoquaux@inria.fr}}
\author[2]{L. Buitinck}
\author[3]{G. Louppe}
\author[1]{O. Grisel}
\author[1]{F. Pedregosa}
\author[4]{A. Mueller}
\affil[1]{Parietal, INRIA, Bat 145 CEA Saclay, 91191 Gif-sur-Yvette,
France}
\affil[2]{ISLA, University of Amsterdam, Science Park 904, Amsterdam, The
Netherlands}
\affil[3]{Montefiore Institute, University of Liège, Liège, Belgium}
\affil[4]{Amazon Development Center Germany, Berlin, Germany}

@@

Scikit-learn aims at bridging the gap between machine-learning research and
applications by providing a library, and not an environment, in a
general-purpose programming language, relying on domain-agnostic data structures
\cite{pedregosa2011}. Emphasis is put on quality and ease of use, which
implies focus on installation issues, documentation, and API design
\cite{buitinck2013ecml}. For the project to be usable in real-world
settings, computational performance is also a priority.

@@

\paragraph{Supervised models: learning to predict.}
%
The goal of supervised models is the prediction of some value of interest.
The corresponding estimators
have a {\tt predict} method, that takes a data matrix $\mathbf{X}$ and
returns a predicted $\mathbf{y}$.

\paragraph{Model evaluation and parameter selection.}
%
The performance of a model measures its ability to correctly
predict new data. Because of overfitting, the \emph{train} data used for
learning
should in general not be used to also evaluate model performance, as it may often
result in overly optimistic estimates of the true prediction error of the model.
Instead, the correct way to obtain an unbiased estimate is to leave out \emph{test} data,
untouched during training and used for model evaluation only.
Alternatively, a \emph{cross-validation} scheme may also be
used, where the data is repeatedly split into \emph{train} and
\emph{test} subsets. Scikit-learn provides integrated support for
cross-validation, as specific iterators defining the train and test
subsets. Several functions and objects accept these iterators as arguments to
perform cross-validation internally. For instance the {\tt
cross\_val\_score} function measures the prediction score of an
estimator. Cross-validation can also be used to tune the meta-parameters
of an estimator, such as the sparsity of a sparse model. For this,
specific estimators, \emph{meta-estimators}, such as the {\tt
GridSearchCV}, take another estimator at construction time, and use
cross-validation internally to set its parameter. When used together with
{\tt cross\_val\_score}, they perform \emph{nested} cross-validation,
\emph{i.e.}~the meta-parameters are set independently of the test data.

@@

In Fig.~\ref{fig:code} we give an example of fully functioning code to
do sentiment polarity classification for movie reviews: given a review,
it outputs whether that review is positive about the movie it concerns.
The code demonstrates the use of pipelines, and also shows how machine
learning ties into other Python modules: downloading, unpacking and
learning from a dataset are all done in one programming language.
This script first fetches a hand-labeled movie review dataset
\cite{pang2004} and unpacks it to disk using standard Python libraries.
It then loads these using scikit-learn data loading functions, makes a
pipeline of a \textsf{tf--idf} feature extractor
\cite{rennie2003tackling} (that turns strings into a sparse matrix based
on word frequencies) and logistic regression, and finally trains the
model. Parameters for the feature extractor and the classifier
were set manually.

\begin{figure*}[b]
% To have the float on the bottom, we need this declared on the page
% before where it is going to be printed
\lstinputlisting{online_learning_example.py}
\caption{On-line learning example: the main loop iterates through batches
of 1000 documents, vectorizing them on the fly and updating the
classifier. Running the example shows that the error on the test set
progressively decreases as data is accumulated.\label{fig:online}}
\end{figure*}

@@

% The citation is for "Heaps' law":
% vocabulary size as a function of collection size.
% Gael, feel free to remove it if you think it's too detailed.
With large collections of text, one faces both challenges:
the dimensionality $p$
tends to increase with sample size $n$, as the number of different words used
is greater in large collections \cite[88--89]{manning2009}.
Beyond the mere size of the data matrix
created by a standard vectorization approach, outlined earlier, another challenge
is that the vectorization must be done in two passes over the documents,
as the size of the output vectors is not known up front.
Here, \emph{feature hashing} can be used
to tackle both of these challenges and produce a streaming vectorizer,
the {\tt HashingVectorizer} in scikit-learn.
Words are run through a (stateless) hash function, rather than a lookup table,
to map words to indices.
Collisions may occur, but the hashing algorithm \cite{weinberger2009}
is specially designed to mitigate their effect.
The dimensionality of the output vectors can be set by the user;
the bigger, the less likely collisions will occur.
%
A full example doing online learning on a large corpus of text is given
in Fig.~\ref{fig:online}.

@@

Scikit-learn has become a reference machine learning toolkit. As such, it
should offer a wide variety of learning algorithms. However, each new
feature, each new line of code, comes with a maintenance cost.
Uncontrolled growth would lead the project to pick up weight until it
came to a crawl. The difficulty lies in defining the project scope and
prioritizing methods. We strive to identify and integrate all major
methods most useful for prediction tasks. We favor time-tested
algorithms and put great care in the choice of default parameters. We put
a lot of effort in making the documentation didactic and
pragmatic. Our
secret ambition is that it can provide an executable alternative to
textbooks, with all the figures generated by code examples.

Machine learning is a very active field of research, with promising
trends such as deep learning, harnessing GPUs or distributed computing
for extra computational power, or extending to new platforms, such as
Android or iOS-based embedded devices. However, as scikit-learn's purpose
is to provide tried-and-true, mostly turn-key, predictive tools, we have
to walk the fine line between supporting powerful techniques and
utilizing our limited project cycles on proven technologies. For
instance, deep neural networks are an emerging tool with a huge
potential, but are still in flux and hard to use without significant expertise.
Similarly, GPGPU technology is promising, but not ready for non-expert use.
The HPC community and industry have largely achieved source-level compatibility with OpenCL
\cite{stone2010opencl},
but performance portability and cross-platform driver support remain
challenging.
%
Support for mobile platforms such as Android is determined by those platforms'
support for Python and the standard C/C++ build chain. Indeed, our basic
execution environment is the scientific Python stack, that is both very
powerful and high-level. The vision of the scikit-learn project is to
bring advances in machine learning to users that that may lack the full
expertise. As a consequence, we focus on seasoned approaches, rather than
implementing ongoing research. We believe that code is an intrinsic part
of the scholarship outcome of scientific research in computational
science \cite{buckheit1995wavelab}, and scikit-learn strives to be akin
to a reference textbook in this research software landscape.
